\cvsection{Professional Background}

\begin{cvparagraph}
My Professional Background is mostly focused on software integration, migration from legacy to new systems, troubleshooting via logging / debugging and automation.
Most of them using Java stack for big projects and Ruby / bash for automation.
\end{cvparagraph}

\cvsection{Recent Companies}

\begin{cventries}

\cventry
{Backend Software Engineer}
{European Computer Telecoms AG}
{Munich, Germany}
{10/2016 - Current}
{
\begin{cvitems}
\item Working on Backend Software development for telecommunication business;
\item Software development and maintenance of Phone Carriers and Contact Center products;
\item Integration efforts focused on several different platforms, mostly on migration of legacy projects and Social Media Integration.
\end{cvitems}
}

\cventry
{IT Specialist}
{Movile}
{Campinas, São Paulo}
{07/2015 - 06/2016}
{
\begin{cvitems}
\item Full-stack software developer (backend, front-end and mobile technologies in a daily basis);
\item Usage of bleeding-edge technologies on highly massive / parallel / distributed computing, for media tracking and complex event processing;
\item Integration efforts on several different platforms (mostly authentication, payments API and mobile apps integration);
\item Agile and self-organized team. Daily duties such as new platform features, bug fixes, application support, pull requests and overall platform monitoring are shared and distributed amongst all team members.
\end{cvitems}
}

\cventry
{Software Solution Architect}
{Avaya Inc.}
{Global}
{06/2012 - 07/2015}
{
\begin{cvitems}
\item Business on telecommunication and contact centre, using Avaya internal products, Java Platform (JEE/JSE) and several open source tools;
\item Responsible for team management, effort estimation, custom software pricing and technical interviews for new software and lead developers;
\item Team members geographically distributed performing their duties mostly via voice and/or video conferencing and collaboration tools;
\item International experience interacting by phone / e-mail with customers and Avaya employees located in Brazil, USA, Canada, India, Argentina, United Kingdom, Germany, Australia, China and Singapore.
\end{cvitems}
}

\cventry
{Systems Architect}
{CFlex}
{Campinas, São Paulo}
{09/2008 - 06/2012}
{
\begin{cvitems}
\item Business on Railroad planning, responsible for overseeing all technical areas of the company;
\item Working as a system integrator. Used tools and technologies: Apache Camel / Spring, Java Swing, JBoss and Oracle / MS-SQL Server;
\item Responsible for technical interviews for new Software Architects, Software and Lead Developers;
\item International experience interacting with customers and employees in Brazil, USA, Canada, Argentina, Bolivia, Chile and Australia.
\end{cvitems}
}
\end{cventries}

\cvsection{Old Background}

\begin{cventries}

\cventry
{Small Business Owner}
{\textbf{[gm]}$^2$ Intelligent Systems}
{Campinas, São Paulo}
{08/2007 - 10/2013}
{
\begin{cvitems}
\item Business on outsourcing, time series forecasting and financial market;
\item Working with Matlab, Social Networks and short-term projects.
\end{cvitems}
}

\cventry
{Software Engineer}
{Ujima Software}
{Campinas, São Paulo}
{08/2007 - 09/2008}
{
\begin{cvitems}
\item Start-up company experience, working with mobile and web applications on Social Networking for Universities (Alumni) at Softex Campinas;
\item Applied Technologies: GWT, AppFuse, Maven, Ant, PostgreSQL and JME.
\end{cvitems}
}

\cventry
{Software Engineer}
{Ci\&T Software}
{Campinas, São Paulo}
{06/2006 - 08/2007}
{
\begin{cvitems}
\item Responsible for Systems development in JEE, technical consultancy, applied innovation and infrastructure analysis;
\item Outsourcing work for several types of customers, mostly on Insurance companies, elevators manufacturers and cosmetics industry.
\end{cvitems}
}

\cventry
{Software Engineer}
{Provider Tech Solutions}
{Recife, Pernambuco}
{05/2005 - 03/2006}
{
\begin{cvitems}
\item Business on Contact Centers and Financial Market;
\item Software Development on banking transaction systems, contact centres, customer services and workforce management.
\end{cvitems}
}

\cventry
{Software Engineer}
{Catholic University of Pernambuco}
{Recife, Pernambuco}
{01/2005 - 05/2005}
{
\begin{cvitems}
\item Working at the Brazilian Digital TV Project;
\item Development of a ITU-T H.264 resolution video transcoder: lowering digital signal resolution / conversion to simple TVs.
\end{cvitems}
}

\cventry
{Software Engineer / Consultant}
{Itautec-Philco R\&D Lab}
{Recife, Pernambuco}
{09/2003 - 12/2004}
{
\begin{cvitems}
\item Business on banking and commercial automation;
\item Provision of consultancy services, Systems development using JEE/JSE/C++ for client/server systems.
\end{cvitems}
}

\cventry
{Researcher}
{Catholic University of Pernambuco}
{Recife, Pernambuco}
{09/2002 - 08/2004}
{
\begin{cvitems}
\item Allocated at the Computer Science R\&D Lab as a Researcher (2003). Working with Scientific Research on optimization and automation of conflicted scheduling solving, by using Linear Programming, scheduling theory and combinatorial algorithms;
\item Allocated at the Computer Science R\&D Lab as a Researcher (2002). Scientific Research in Applied Mathematics and Computational Simulation of the diffusion behavior of an oil spill over the sea;
\item \textit{Awarded as the best work of applied scientific research at UNICAP in 2003}.
\end{cvitems}
}

\end{cventries}

\pagebreak
