\documentclass[11pt, a4paper]{awesome-cv}

\colorlet{awesome}{awesome-orange}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
\usepackage{xcolor}

\hypersetup{
  colorlinks=false,
  linkbordercolor=red,
  pdfborderstyle={/S/U/W 1}
}

\input{placeholder.tex}

\recipient
  {From: \myname}
  {To: \company~- Recruitment Team}
\letterdate{\today}
\lettertitle{Job Application for \job}
\letteropening{\\Dear \hrmanager,}
\letterclosing{Sincerely, \\\\ \signature}
\letterenclosure[Attached]{Curriculum Vitae}

\begin{document}

\makecvheader

\makecvfooter
  {\today}
  {\completename~~~·~~~Cover Letter}
  {}

\makelettertitle

\begin{cvletter}

The purpose of this letter is to express my interest about your job post at \website~for an experienced IT professional.
With a Bachelor’s degree in Computer Science and two decades of hands­on experience at several platforms
and programming languages, creating and implementing software applications throughout all software lifecycle / ecosystems,
I am confident that I would be a valuable person to \company.

\lettersection{Why \company?}

From the Job Description I've seen at \website, I would say the technologies you have been working are very close to the ones I've been
working for many years. I have large experience on software platforms, doing several major back-end integrations
on social media (facebook, twitter and google APIs) as well as payment integration (Stripe, Giftcards), user authentication and media tracking.
Most of those things were made from scratch, based on micro-services architecture, working
transparently and ready to scale (both vertically and horizontally).

I also played a leadership role at Avaya (Solution Architect),
with contact centre products and IVR technologies, coordinating a software development team in India and doing follow up through daily calls.
During this time, I was part of the team responsible for the
HP Global contact Centre migration from Cisco to Avaya products.

Besides, I have plenty of experience on several different businesses, which can bring to \company~different standpoints
and best practices from different markets.

\lettersection{Why Me?}

Reading your Job Description and bringing to the table the will on putting my brain and hands available for \company,
I strongly believe that \company~ is the best match for my professional expectations.
Also, in order to introduce myself properly in terms of source code, once you are looking for someone
with coding skills, you can see the repositories I have special interest and a few code samples
I've contributed \href{https://github.com/glauciom}{at github}.

From my \website~ profile and my attached CV, you will be able to get more details
about the companies / projects I've been working and my overall experience with Computer Science.

Thank you for your time and consideration. I’m looking forward to speak with you about this opportunity.

\end{cvletter}
\makeletterclosing
\end{document}
